Symmetric Peer-to-Peer Applications

### 2022-08-20 tpd-22.tex
...

\IEEEtitleabstractindextext{%
\begin{abstract}
In multi-node collaborative applications, users can interact remotely and
share the exact same experience as if they were in a single machine.
%
In this work, we propose a middleware for \emph{symmetric peer-to-peer
applications} in which decentralized instances can broadcast asynchronous
events and yet conform to identical behavior.
%
Nodes are allowed to join and leave the network at any time.
Application developers must adhere to a restricted API, which is
deterministic, stateless, and only supports pre-allocated memory.
%
The middleware is responsible for synchronizing the events in a global shared
timeline across the network.
Based on memory snapshots and deterministic simulation, a ``time machine'' can
rollback conflicting nodes to resynchronize their state.
%
TODO: application, results
\end{abstract}

@@

>>>>

\IEEEtitleabstractindextext{%
\begin{abstract}
In multi-node collaborative applications, such as shared online documents,
users can interact remotely and yet share the exact same experience as if they
were in a single machine.
%
In this work, we propose a middleware for \emph{symmetric peer-to-peer
applications} in which decentralized instances can broadcast asynchronous
events and yet conform to identical behavior.
%
Nodes are allowed to join and leave the network at any time.
Application developers must adhere to a restricted API, which is
deterministic, stateless, and only supports pre-allocated memory.
%
The middleware is responsible for synchronizing the events in a global shared
timeline across the network.
Based on memory snapshots and deterministic simulation, a ``time machine'' can
rollback conflicting nodes to resynchronize their state.
%
TODO: application, results
\end{abstract}

@@

In this section, we describe the architecture of our middleware and also the
API in which developers need to conform.
%
We guide our discussion through a didactic example in which multiple users use
the arrow keys to change the direction of a moving rectangle.

- same keys, same behavior, pause at the same time

we show how a

- sym
- ids
- walk back-forth
- vector clocks
- dynamic net
- re-connect
- late join
